---
title: "Supplemental Models"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(mlogit)
library(dplyr)
library(MASS)
library(tidyverse)
```

Reference guide for ordered logit models: https://stats.oarc.ucla.edu/r/dae/ordinal-logistic-regression/
Reference guide for multinomial probit models: https://cran.r-project.org/web/packages/mlogit/vignettes/c6.mprobit.html 

## Data Dowload

```{r}
full_data = read.csv("../../Private/data_cleaned.csv")
```

## Model 1
### Sector and Subfield vs. GPUs Used in Most Compute-Intensive Project

```{r}
df <- full_data %>%
  dplyr::select(CompGPUs, Sector, CV, NLP, Robotics, RL, Other) %>%
  drop_na() %>%
  filter(Sector %in% c('Academia', 'Industry')) %>%
  mutate(CompGPUs = as.factor(CompGPUs))

gpu.orderedmodel <- polr(CompGPUs ~ ., data = df, Hess = T)

output <- coef(summary(gpu.orderedmodel))
p <- pnorm(abs(output[, 't value']), lower.tail = F) * 2
output <- cbind(output, "p value" = p)
ci <- rbind(confint(gpu.orderedmodel), matrix(, nrow = 6, ncol = 2))
output <- cbind(output, ci)

output
```

## Model 2
### Sector and Subfield vs. Cost of Compute in Most Compute-Intensive Project

```{r}
df <- full_data %>%
  dplyr::select(CompCost, Sector, CV, NLP, Robotics, RL, Other) %>%
  drop_na() %>%
  filter(Sector %in% c('Academia', 'Industry')) %>%
  mutate(CompCost = as.factor(CompCost))

cost.orderedmodel <- polr(CompCost ~ ., data = df, Hess = T)

output <- coef(summary(cost.orderedmodel))
p <- pnorm(abs(output[, 't value']), lower.tail = F) * 2
output <- cbind(output, "p value" = p)
ci <- rbind(confint(cost.orderedmodel), matrix(, nrow = 5, ncol = 2))
output <- cbind(output, ci)

output
```

## Model 3
### Sector and Subfield Effects on Concern about Future Contributions

```{r}
df <- full_data %>%
  dplyr::select(ContributionConcern, Sector, CV, NLP, Robotics, RL, Other) %>%
  drop_na() %>%
  filter(Sector %in% c('Academia', 'Industry')) %>%
  mutate(ContributionConcern = as.factor(ContributionConcern))

concern.orderedmodel <- polr(ContributionConcern ~ ., data = df, Hess = T)

output <- coef(summary(concern.orderedmodel))
p <- pnorm(abs(output[, 't value']), lower.tail = F) * 2
output <- cbind(output, "p value" = p)
ci <- rbind(confint(concern.orderedmodel), matrix(, nrow = 4, ncol = 2))
output <- cbind(output, ci)

output
```

## Model 4
### Subfield and GPU Utilization Effects on Concern about Future Contributions 

```{r}
df <- full_data %>%
  filter(Sector == 'Academia') %>%
  dplyr::select(ContributionConcern, CV, NLP, Robotics, RL, Other, CompGPUs) %>%
  drop_na() %>%
  mutate(ContributionConcern = as.factor(ContributionConcern),
         CompGPUs = as.factor(CompGPUs))

concern.gpus.model <- polr(ContributionConcern ~ ., data = df, Hess = T)

output <- coef(summary(concern.gpus.model))
p <- pnorm(abs(output[, 't value']), lower.tail = F) * 2
output <- cbind(output, "p value" = p)
ci <- rbind(confint(concern.gpus.model), matrix(, nrow = 4, ncol = 2))
output <- cbind(output, ci)

output
```

## Model 5
### GPU Utilization Impact on Budget Priorities

```{r}
df <- full_data %>%
  filter(PrioritySimplified != '', CompGPUs != '') %>%
  mutate(Priority = as.factor(PrioritySimplified)) %>%
  dplyr::select(Priority, CompGPUs) %>%
  dfidx(choice = 'Priority', shape = 'wide')

gpu.probit <- mlogit(Priority ~ 1 | CompGPUs, data = df, reflevel = 'Talent', alt.subset = c('Compute', 'Talent', 'Data'), probit = T)
summary(gpu.probit)
```

## Model 6
### GPU Utilization, Sector, and Subfield Impact on Budget Priorities

```{r}
df <- full_data %>%
  filter(PrioritySimplified != '', CompGPUs != '', Sector %in% c('Industry', 'Academia'), 
         CV | Robotics | NLP | RL | Other > 0) %>%
  mutate(Priority = as.factor(PrioritySimplified), 
         Industry = .$Sector == 'Industry') %>%
  dplyr::select(Priority, CompGPUs, Industry, CV, Robotics, NLP, RL, Other) %>%
  dfidx(choice = 'Priority', shape = 'wide')

full.probit <- mlogit(Priority ~ 1 | CompGPUs + Industry + CV + Robotics + NLP + RL + Other, 
                      data = df, reflevel = 'Talent', alt.subset = c('Compute', 'Talent', 'Data'), probit = T)
summary(full.probit)
```

